%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-skyblue}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Dr. Rhian }{Davies}
\address{Lancaster, UK}
\mobile{07805 871708} 
%%% Social
\email{thetrianglegirl@gmail.com}
\homepage{trianglegirl.rbind.io}
\github{trianglegirl}
\linkedin{trianglegirl}
%%% Optionals
\position{Statistician {\enskip\cdotp\enskip} Data Scientist {\enskip\cdotp\enskip} STEM Communicator  {\enskip\cdotp\enskip} R Geek }
%\position{Software Engineer{\enskip\cdotp\enskip}Security Expert}
%\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Esther Gillespie, CEO}
  {Jumping Rivers}
\letterdate{\today}
\lettertitle{Job Application for Data Scientist at Jumping Rivers}
\letteropening{Dear Esther,}
\letterclosing{Kind Regards,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Dr. Rhian Davies~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
%\cvparagraph{This job sounds awesome}

I was very excited to see your data scientist position advertised. With my broad data science experience, passion for learning and love of R, I believe I can support Jumping Rivers in developing and delivering your existing courses, and providing high-quality consultancy. I admire your ethos of giving back to the community, through meet-ups and supporting conferences as it is something that I value too.

\cvparagraph{How I can help Jumping Rivers}
As a data scientist, I have worked closely with varied domain experts including physicists, psychologists, game designers and engineers. Successful projects include classifying accelerometer data and validating psychometric models for game-based assessment. I introduced my Unilever team to RMarkdown as a laboratory notebook, a practice which they have since adopted within the team, and at Arctic Shores I encouraged and supported the psychologists to develop a reproducible workflow in R. At Digital Rail I have gained experience in consultancy, creating visualisation tools in Shiny to help engineers explore the health of their fleet. I'm a confident communicator, and in my role as an RSS Statistical Ambassador, I have received media training, helped journalists communicate facts and providing consultancy for a Panorama documentary. I learn best through teaching, and have varied experience including formal University tuition, supporting R courses for industry and delivering public outreach talks.

\cvparagraph{Why I want to work for Jumping Rivers}
I would love to work for Jumping Rivers as the combination of delivering training courses and providing statistical consultancy is a truly exciting role for me. The best thing for me about being a statistician is being able to help people understand their data and this seems to be at the core of Jumping Rivers. I believe the role will challenge me to keep learning and actively develop my skills. As well as statistical knowledge, I can bring enthusiasm, a passion for learning and appetite for challenge to the Jumping Rivers team.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
